---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Global Document Options
```{r setup, cache=FALSE}
library(knitr)

# Define Significant Digits for Output
opts_chunk$set(R.options=options(digits = 2))

# Override the Inline Hook for Significant Digits to Match
# From Stack Overflow -- http://bit.ly/2263m7g
inline_hook <- function(x) {
    if(is.numeric(x)) x <- round(x, 2)
    paste(as.character(x), collapse=", ")
}
knit_hooks$set(inline = inline_hook)
```

## Required Libraries
```{r required_libs, message=FALSE}
library(dplyr)
library(ggplot2)
library(ggthemes)
```

## Loading and preprocessing the data
```{r load_parse, echo=TRUE}
# Load CSV Activity Data and Define Data Types
df <- read.csv(unz("activity.zip", "activity.csv"), 
               colClasses = c("steps" = "integer",
                              "date" = "Date",
                              "interval" = "integer"))

# Review Data Frame Composition
str(df)

###
# Build Means and Sum Vectors for Later Use
###

# Vectpr of Step Sums by Day
day.sums = df %>% 
  group_by(date) %>% 
  summarize(steps = sum(steps))

# Vector of Means by 5 Minute Interval
interval.means = df %>% 
  group_by(interval) %>% 
  summarize(steps = mean(steps, na.rm = T))
```

## What is mean total number of steps taken per day?

```{r mean_steps, echo=TRUE, message=FALSE, warning=FALSE}
ggplot(day.sums, aes(steps)) + 
  geom_histogram(alpha = 0.5, binwidth = 1000) +
  theme_hc() +
  ggtitle("Steps per Day Histogram") +
  xlab("Total Amount of Steps per Day")
```

### Mean and Median Steps by Day Without NAs

The mean steps per day without NAs is `r mean(day.sums$steps, na.rm = T)` and 
the median steps per day without NAs is `r median(day.sums$steps, na.rm = T)`.

## What is the average daily activity pattern?
```{r avg_daily_activity, echo=TRUE}
ggplot(interval.means, aes(x = interval, y = steps)) +
  geom_line() +
  theme_hc() +
  ggtitle("Average Daily Activity Pattern") +
  xlab("Time Interval") +
  ylab("Mean Steps")
```


## Imputing missing values
```{r fill_missing, echo=TRUE}
```


## Are there differences in activity patterns between weekdays and weekends?
```{r weekday_weekend_contrast, echo=TRUE}
```